Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-12-04 README.Rmd
removed to do list
fixed some file paths

## To Do

- Prepare for submission (make sure to update date on cover letter)
- Upload the files for submission and submit
- Save a "snapshot" of the repo in the CyBox folder

@@

- [01-raw-file-compression.Rmd](code/01-raw-file-compression.Rmd)/[.html](code/01-raw-file-compression.html) contains R code for compressing the static figure used in the manuscript and accessing and compressing the raw bullet data to be uploaded to GitHub
- [02-data-preparation.Rmd](code/02-data-preparation.Rmd)/[.html](code/02-data-preparation.html) contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the manuscript and saves zip versions of the prepared data sets to be uploaded to GitHub
- [03-submission-steps.Rmd](code/03-submission-steps.Rmd)/[.html](code/03-submission-steps.html) contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal

>>>>

@@

- [01-raw-file-compression.Rmd](code/01-raw-file-compression.Rmd)/[.md](code/01-raw-file-compression.md) contains R code for compressing the static figure used in the manuscript and accessing and compressing the raw bullet data to be uploaded to GitHub
- [02-data-preparation.Rmd](code/02-data-preparation.Rmd)/[.md](code/02-data-preparation.md) contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the manuscript and saves zip versions of the prepared data sets to be uploaded to GitHub
- [03-submission-steps.Rmd](code/03-submission-steps.Rmd)/[.md](code/03-submission-steps.md) contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal
